---
title: "Movie Revenue Analysis"
author:" Selenge Tulga"
date: "2023-12-14"
output: 
  pdf_document:
    number_sections: true
bibliography: references.bib
csl: ieee.csl
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(dev = "png",
                      dpi = 300,
                      echo = FALSE,
                      cache = TRUE)

library(ggplot2)
library(dplyr)
library(MASS)
library(corrplot)
library(caret)
```

\vspace{5pt}

# Introduction

Every dataset has a story to tell, and ours is no exception. It's a tale of trends and fluctuations, of insights and surprises, waiting to be articulated. 

# Dataset

To conduct this research, we utilize information obtained from the IMDB dataset, which is accessible on Kaggle.
```{r}
movies <- read.csv("/Users/selengetulga/Downloads/Fall 2023/DSCC 462/Final/TMDB_movie_dataset_v11.csv")

sprintf("Dataset has %d rows and %d columns", nrow(movies), ncol(movies))
```
# Data Processing

Before moving forward with our analysis, we first need to process the dataset.

## Attribute Selection

The dataset contains 31 columns, all of which we don't need. So, we first select the columns we need and discard the rest.

```{r Attribute_Selection, echo=T}
movies <- movies[c("id", "title", "vote_average", "vote_count", "release_date", "revenue", "runtime", "adult", "budget", "original_language",
           "popularity", "genres", "production_companies", "production_countries")]
sprintf("Number of columns in dataset: %d", ncol(movies))
```

Let's first see what percentage of the columns are missing.We have to fill in the
missing values as well as we can.

```{r Imputation Missing value percentage for each column, echo=T}
missing_percentage <- colMeans(is.na(movies)) * 100
sorted_missing <- sort(missing_percentage, decreasing = TRUE)

formatted_missing <- sprintf("%2.6f%%", sorted_missing)

result_df <- data.frame(Column = names(sorted_missing), 
                        MissingPercentage = formatted_missing)
print(result_df)
```
Some budget, revenue value are between 1 and 100. Now we set limitation in some fields. Movie's budget and revenue are greater than 10K and voting count is greater than 400 people.

```{r}
df_movies= movies[movies$budget > 10000 & movies$revenue> 10000 & movies$popularity> 0 & movies$runtime> 0 & movies$vote_count>400,] 
dim(df_movies)
```
## Custom Columns

### Ration of budget and revenue

$$
ratio = revenue/ budget
$$
```{r Custom_Columns Distance from Earth, echo=T}
df_movies$ratio <- (df_movies$revenue/df_movies$budget)
summary(df_movies$ratio)
```

### Movie budget types


### Revenue Type


### Movie Release Season


# Exploratory Data Analysis

In this section we'd like to go over the different factors that play into movie revenue. In particular, we try to answer the following questions:

1. **Distance**: It's easier to mine asteroids the closer they are. On average, is the mean distance of NEO asteroids less than 1 AU?

2. **Material**: Metallic resources are more valuable and thus metallic asteroids should be sought out for mining. Does NEO asteroids have proportionately more metallic asteroids than non-NEO asteroids?

3. **Asteroid size**: Large asteroids have more resources than smaller asteroids. On average, is the mean diameter of NEO asteroids smaller than non-NEO asteroids?

4. **Diameter difference**: There are 4 different types of NEO asteroids. Is there a significant difference between their average diameter?

5. **Value difference**: From a material value standpoint, which NEO type is the best to mine?


```{r}
n_pop <- ceiling(log2(length(df_movies$popularity))) + 1
sprintf("Bin number of popularity: %d", n_pop)

n_rev <- ceiling(log2(length(df_movies$revenue))) + 1
sprintf("Bin number of revenue: %d", n_pop)

n_bud <- ceiling(log2(length(df_movies$budget))) + 1
sprintf("Bin number of budget: %d", n_pop)

n_bud <- ceiling(log2(length(df_movies$runtime))) + 1
sprintf("Bin number of runtime: %d", n_pop)
```

```{r}
e_budget = (df_movies$budget)/ 1e6
```


```{r}
e_revenue = (df_movies$revenue)/ 1e6
relative_freq_table <- prop.table(table(e_budget))
absolute_freq_table <- table(e_budget)
```


```{r}

library(e1071)
library(DescTools)
mean_runtime <- mean(df_movies$runtime)
median_runtime <- median(df_movies$runtime)
mode_runtime <- as.numeric(names(sort(table(df_movies$runtime), decreasing = TRUE)[1]))
trimmed_mean_runtime <- mean(df_movies$runtime, trim = 0.1)

# Dispersion
iqr_runtime <- IQR(df_movies$runtime)
variance_runtime <- var(df_movies$runtime)
cv_runtime <- sd(df_movies$runtime) / mean(df_movies$runtime)
skewness_runtime <- skewness(df_movies$runtime)

print(paste("Mean:", mean_runtime))
print(paste("Median:", median_runtime))
print(paste("Mode:", mode_runtime))
print(paste("Trimmed Mean (10%):", trimmed_mean_runtime))
print(paste("IQR:", iqr_runtime))
print(paste("Variance:", variance_runtime))
print(paste("Coefficient of Variation:", cv_runtime))
print(paste("Skewness:", skewness_runtime))
```

```{r}
#Budget statistic
# Center
mean_budget <- mean(df_movies$budget)
median_budget <- median(df_movies$budget)
mode_budget <- Mode(df_movies$budget)
trimmed_mean_budget <- mean(df_movies$budget, trim = 0.1)

# Dispersion
iqr_budget <- IQR(df_movies$budget)
variance_budget <- var(df_movies$budget)
cv_budget <- sd(df_movies$budget) / mean(df_movies$budget)
skewness_budget <- skewness(df_movies$budget)

print(paste("Mean:", mean_budget))
print(paste("Median:", median_budget))
print(paste("Mode:", mode_budget))
print(paste("Trimmed Mean (10%):", trimmed_mean_budget))
print(paste("IQR:", iqr_budget))
print(paste("Variance:", variance_budget))
print(paste("Coefficient of Variation:", cv_budget))
print(paste("Skewness:", skewness_budget))

```
```{r}
#Revenue statistic
# Center
mean_revenue <- mean(df_movies$revenue)
median_revenue <- median(df_movies$revenue)
mode_revenue <- as.numeric(names(sort(table(df_movies$revenue), decreasing = TRUE)[1]))
trimmed_mean_revenue <- mean(df_movies$revenue, trim = 0.1)

# Dispersion
iqr_revenue <- IQR(df_movies$revenue)
variance_revenue <- var(df_movies$revenue)
cv_revenue <- sd(df_movies$budget) / mean(df_movies$revenue)
skewness_revenue <- skewness(df_movies$revenue)

print(paste("Mean:", mean_revenue))
print(paste("Median:", median_revenue))
print(paste("Mode:", mode_revenue))
print(paste("Trimmed Mean (10%):", trimmed_mean_revenue))
print(paste("IQR:", iqr_revenue))
print(paste("Variance:", variance_budget))
print(paste("Coefficient of Variation:", cv_revenue))
print(paste("Skewness:", skewness_revenue))
```
```{r}
#Popularity statistic
# Center
mean_popularity <- mean(df_movies$popularity)
median_popularity <- median(df_movies$popularity)
mode_popularity <- as.numeric(names(sort(table(df_movies$popularity), decreasing = TRUE)[1]))
trimmed_mean_popularity <- mean(df_movies$popularity, trim = 0.1)

# Dispersion
iqr_popularity <- IQR(df_movies$popularity)
variance_popularity <- var(df_movies$popularity)
cv_popularity <- sd(df_movies$popularity) / mean(df_movies$popularity)
skewness_popularity <- skewness(df_movies$popularity)

print(paste("Mean:", mean_popularity))
print(paste("Median:", median_popularity))
print(paste("Mode:", mode_popularity))
print(paste("Trimmed Mean (10%):", trimmed_mean_popularity))
print(paste("IQR:", iqr_popularity))
print(paste("Variance:", variance_popularity))
print(paste("Coefficient of Variation:", cv_popularity))
print(paste("Skewness:", skewness_popularity))
```
```{r}
#Vote statistic
# Center
mean_vote_average <- mean(df_movies$vote_average)
median_vote_average <- median(df_movies$vote_average)
mode_vote_average <- as.numeric(names(sort(table(df_movies$vote_average), decreasing = TRUE)[1]))
trimmed_mean_vote_average <- mean(df_movies$vote_average, trim = 0.1)

# Dispersion
iqr_vote_average <- IQR(df_movies$vote_average)
variance_vote_average <- var(df_movies$vote_average)
cv_vote_average <- sd(df_movies$vote_average) / mean(df_movies$vote_average)
skewness_vote_average <- skewness(df_movies$vote_average)

print(paste("Mean:", mean_vote_average))
print(paste("Median:", median_vote_average))
print(paste("Mode:", mode_vote_average))
print(paste("Trimmed Mean (10%):", trimmed_mean_vote_average))
print(paste("IQR:", iqr_vote_average))
print(paste("Variance:", variance_vote_average))
print(paste("Coefficient of Variation:", cv_vote_average))
print(paste("Skewness:", skewness_vote_average))
```
```{r}
#Vote-count statistic
# Center
mean_vote_count <- mean(df_movies$vote_count)
median_vote_count <- median(df_movies$vote_count)
mode_vote_count <- as.numeric(names(sort(table(df_movies$vote_count), decreasing = TRUE)[1]))
trimmed_mean_vote_count <- mean(df_movies$vote_average, trim = 0.1)

# Dispersion
iqr_vote_count <- IQR(df_movies$vote_count)
variance_vote_count <- var(df_movies$vote_count)
cv_vote_count <- sd(df_movies$vote_count) / mean(df_movies$vote_count)
skewness_vote_count <- skewness(df_movies$vote_count)

print(paste("Mean:", mean_vote_count))
print(paste("Median:", median_vote_count))
print(paste("Mode:", mode_vote_count))
print(paste("Trimmed Mean (10%):", trimmed_mean_vote_count))
print(paste("IQR:", iqr_vote_count))
print(paste("Variance:", variance_vote_count))
print(paste("Coefficient of Variation:", cv_vote_count))
print(paste("Skewness:", skewness_vote_count))
```


```{r}
# Scatterplot of Budget

plot(e_budget, e_revenue, main = "Scatterplot", xlab = "Budget", ylab = "Revenue")
```
```{r}
# Covariance
covariance <- cov(df_movies$budget, df_movies$revenue)
print(paste("Covariance:", covariance))
```

```{r}
# Scatterplot of Budget
plot(df_movies$runtime, df_movies$vote_average, main = "Scatterplot of runtime and vote", xlab = "runtime", ylab = "Vote")
```

```{r}
# Histogram with mean and median lines
hist(df_movies$budget, main = "Histogram of budget", xlab = "Budget", col = "lightblue", border = "black", xlim = c(0, max(df_movies$budget)))
abline(v = mean_budget, col = "red", lwd = 2)
abline(v = median_budget, col = "blue", lwd = 2)
abline(v = mode_budget, col = "green", lwd = 2)

```

```{r}
# Histogram with mean and median lines
hist(df_movies$revenue, main = "Histogram of revenue", xlab = "Budget", col = "lightblue", border = "black", xlim = c(0, max(df_movies$revenue)))
abline(v = mean_revenue, col = "red", lwd = 2)
abline(v = median_revenue, col = "blue", lwd = 2)
abline(v = mode_revenue, col = "green", lwd = 2)
```
```{r}
# Histogram with mean and median lines
hist(df_movies$runtime, main = "Histogram of runtime", xlab = "Budget", col = "lightblue", border = "black", xlim = c(0, max(df_movies$runtime)))
abline(v = mean_runtime, col = "red", lwd = 2)
abline(v = median_runtime, col = "blue", lwd = 2)
abline(v = mode_runtime, col = "green", lwd = 2)
```

```{r}
qqplot(qnorm(ppoints(nrow(df_movies))), df_movies$budget,
       main = "Quantile Plot",
       xlab = "Theoretical Quantiles",
       ylab = "Sample Quantiles")

```
```{r}
(unique(df_movies$status))
```




```{r}
var_test <- chisq.test(df_movies$budget)
print(var_test)
```
```{r}
prop_test <- prop.test(sum(df_movies$revenue > 0.01), length(df_movies$revenue))
print(prop_test)
```
```{r}
regression_model <- lm(revenue ~ budget, data = df_movies)
print(regression_model)
```
```{r}
anova_result <- aov(revenue ~ factor(original_language), data = df_movies)
print(anova_result)
```

```{r}
correlation_test <- cor.test(df_movies$budget, df_movies$revenue, method = "pearson")
print(correlation_test)
```


```{r}
multiple_regression_model <- lm(revenue ~ budget + vote_average, data = df_movies)
print(multiple_regression_model)
```

